AIS

### 2023-05-11 02_AIS.Rmd
distance function added

library(tidyverse)
library(sf)
library(gganimate)
#install.packages("remotes")
#remotes::install_github("skgrange/gissr")
#devtools::install_github("skgrange/gissr")
library(gissr)

# Function
# Speeding up st_intersection (from https://github.com/r-spatial/sf/issues/801)

@@

# 
(geosphere::distHaversine(AIS_within_buff[9:20,], pois))/1000
```

>>>>

library(tidyverse)
library(sf)
library(gganimate)
#install.packages("remotes")
#remotes::install_github("skgrange/gissr")
#devtools::install_github("skgrange/gissr")
library(gissr)
```

```{r}
# Function
# Speeding up st_intersection (from https://github.com/r-spatial/sf/issues/801)

@@

# 
ship_dist <- (geosphere::distHaversine(AIS_within_buff@coords[10:13,], pois))/1000
cbind(AIS_within_buff@data[10:13,], ship_dist)
```
